---
title: "ANA 515 Assignment 2"
author: "Yuening (Ariel) Wang"
date: "2023-06-18"
output: html_document
---
The data used of this report is the free data set found on Kaggle customer information of a hotel. It includes the customer emails, credit card number, room type, amenities fee, check-in and check-out date, room rate and billing address. I wish to use this data to research what is the customer demographic and hope to see what ad we should put out and attract more high value customer. This data set is saved in CSV file and the delimiter is ‘,’. 


```{r install, echo=TRUE}
#set up packages
library(tidyverse)
library(dplyr)
library(knitr)
```
Reading the data into R
```{r getdata, echo=TRUE}
#Used dplyr package to read in the data
data <-read.csv("/Users/wangyuening/Desktop/McDaniel /Data Storage/Assignment 2/hotel_guests_dataset.csv")

```
Clean the data
```{r clean data, echo=TRUE}
#change the card number from scientific number to text
data <- data %>%
  mutate(credit_card_number = format(credit_card_number, scientific = FALSE))
```
```{r change_name,echo=TRUE}
#Changing the column name 'X' to 'Record#' 
data <- data %>%
  rename('Record#' = X)
```
```{r change to date data,echo=TRUE}
#change the checkin and check out date to date format
data$checkin_date <- as.Date(data$checkin_date, format = "%d %b %Y")
data$checkout_date <- as.Date(data$checkout_date, format = "%d %b %Y")
```

```{r filter data, echo=TRUE}
# There are some rows that has checkout data earlier than checkin date, which is not righ, so we need to filtered out the rows that the checkout_data is earlier than checkin_data
filtered_data <- data %>%
  filter(checkout_date > checkin_date)
```
```{r add duration,echo=TRUE}
#Add a column to calculate the duration of a customer's stay
filtered_data <- filtered_data %>%
  mutate(duration_days= as.numeric(difftime(checkout_date, checkin_date, units = "days")))
```

Characteristics of the data

This dataframe has `r nrow(filtered_data)` rows and `r ncol(filtered_data)` columns. The names of the columns and a brief description of each are in the table below:

```{r table,echo=TRUE}
# Get the column names and descriptions
column_names <- colnames(filtered_data)
column_descriptions <- c("Record# of each transaction record", "Guest'eamil", "whether the cusotmer has rewards point","What room did the customer stayed","Whether customer has amenities fee","Checkin data for this transaction","Checkout data for this transaction","Room rate for each customer","The billing address of the customer","The credit card number of the customer","how many days the customer stayed")  # Provide descriptions for each column

# Combine column names and descriptions into a data frame
summary_table <- data.frame("Column Name" = column_names, "Description" = column_descriptions)

# Create the table using kable
table <- kable(summary_table)

print(summary_table)
```
Summary statistics
```{r pick 3 columns, echo=TRUE}
#pickup out 3 columes
filtered_data2 <- filtered_data %>%
  select(amenities_fee, room_rate, duration_days)
```
```{r summary data, echo=TRUE}
#Summary 
summary_info <-summary(filtered_data2)
summary_info
```
